Countering language attrition with PanLex and the Web of Data

### 2014-03-09 panlex-rdf-paper/2012/MLOD_PanLex/paper_v5.tex
updated figure 1
- redrew png image as svg
- added bigger arrow labels
updated figure 2
- added real world data

\begin{figure}
  \centering
  \includegraphics[width=0.42\textwidth]{images/schema_new.png}
  \caption{The PanLex database schema}
  \label{fig:db-schema}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.46\textwidth]{images/pdf/ontology.pdf}
\caption{Overview of the PanLex RDF Vocabulary}
\label{fig:vocabulary}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.42\textwidth]{images/pdf/db_schema.pdf}
  \caption{The PanLex database schema}
  \label{fig:db-schema}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.46\textwidth]{images/pdf/ontology_new.pdf}
% Query for ontology_new.pdf
%SELECT * WHERE {
%  ?den plx:denotationMeaning ?mea .
%  ?den plx:denotationExpression ?expr .
%  ?expr rdfs:label ?exprlbl .
%  ?mea plx:meaningDefinition ?def .
%  ?mea plx:approver ?app.
%  ?def plx:languageVariety <http://ld.panlex.org/plx/languageVariety/187> .
%  ?def rdfs:label ?dtx .
%  ?den plx:denotationExpression <http://ld.panlex.org/plx/expression/355621> .
%  ?app dc:title ?dctitle .
%  ?app plx:quality ?plxquality .
%  ?app dc:publisher ?dcpublisher .
%  ?app dc:date ?dcdate .
%  ?app rdfs:label ?rdfslabel .
%  ?app foaf:homepage ?foafhomepage .
%  ?app dc:creator ?dccreator .
%  ?app plx:registrationDate ?regdate .
%  ?app plx:license <http://ld.panlex.org/plx/license/mi> .
%  <http://ld.panlex.org/plx/license/mi> rdfs:label ?liclbl .
%  OPTIONAL { ?app dbpedia-owl:isbn ?dboisbn . }
%  OPTIONAL { ?den plx:wordClass ?wordclass . }
%}
\caption{Example of the PanLex RDF vocabulary showing one meaning of the expression `between' and the corresponding source and definition}
\label{fig:vocabulary}
\end{figure}
